---
title: "Combining Fruit NIR Absorbance and Diamter Data"
author: "Jimmy Larson"
date: "6/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This file describes the process for combining NIR absorbance and diameter data for fruit measured as a part of a project to predict fruitlet abscission rates following a chemical thinner application in the spring of 2021. Fruit diameter taken with calipers at it's widest point and NIR spectra was captured with a FELIX F750 Vis/NIR handheld spectrometer for each fruit. Chemical thinner was applied on May 2. Data was collected on the following dates:

* April 28

* May 1

* May 5

* May 7

* May 9 

* May 11

* May 14

NIR absorbance data was exported to a csv file using the F750 data viewer program. The spectra for each individual fruit is a row in a data frame for each measurement date, which were each read in, along with fruit diameters.

```{r, echo=FALSE, warning=FALSE, include=FALSE}
## packages----
library(tidyverse)
library(lubridate)
## read in data ----
nir1 <- read_csv("data/2021/honeycrisp/felix/meas1_absorbance.csv")
nir2 <- read_csv("data/2021/honeycrisp/felix/meas2_absorbance.csv")
nir3 <- read_csv("data/2021/honeycrisp/felix/meas3_absorbance.csv")
nir4 <- read_csv("data/2021/honeycrisp/felix/meas4_absorbance.csv")
nir5 <- read_csv("data/2021/honeycrisp/felix/meas5_absorbance.csv")
nir6 <- read_csv("data/2021/honeycrisp/felix/meas6_absorbance.csv")
nir7 <- read_csv("data/2021/honeycrisp/felix/meas7_absorbance.csv")
diam <- read_csv("data/2021/honeycrisp/diams.csv")
```
## Cleaning NIR data

Before combining data, dates were added to each NIR data frame...

```{r, warning=FALSE}
nir1 %>%
  mutate(measDate = ymd(20210428)) -> nir1
nir2 %>%
  mutate(measDate = ymd(20210501)) -> nir2
nir3 %>%
  mutate(measDate = ymd(20210505)) -> nir3
nir4 %>%
  mutate(measDate = ymd(20210507)) -> nir4
nir5 %>%
  mutate(measDate = ymd(20210509)) -> nir5
nir6 %>%
  mutate(measDate = ymd(20210511)) -> nir6
nir7 %>%
  mutate(measDate = ymd(20210514)) -> nir7
```

Then, rep and cluster number were extracted from each filename (factor - Filename) to create a variable of each. This was done using str_extract() within mutate().

```{r, warning=FALSE}
nir1 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir1
nir2 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir2
nir3 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir3
nir4 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir4
nir5 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir5
nir6 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir6
nir7 %>%
  mutate(rep = str_extract(Filename, "R([1-5])"),
         cluster = str_extract(Filename, "S[:digit:]{1,}(?=_)")) -> nir7
```

Finally, fruit number, counting up from 1, was added for each cluster mesured. This was done to make it easier to match NIR and diamter data.

```{r, warning=FALSE}
nir1 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir1
nir2 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir2
nir3 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir3
nir4 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir4
nir5 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir5
nir6 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir6
nir7 %>%
  group_by(rep, cluster) %>%
  mutate(fruit = row_number()) %>%
  select(rep, cluster, fruit,1:313) -> nir7
```

Each NIR date data frame was then combined with rbind().

```{r, warning=FALSE}
nir <- rbind(nir1, nir2, nir3, nir4, nir5, nir6, nir7)
```

## Cleaning Fruit Diameter Data

A long form of the fruitlet diameter data was first created...

```{r, warning=FALSE}
diam %>%
  gather('meas1', 'meas2', 'meas3', 'meas4', 'meas5', 'meas6', 'meas7', key = "meas", value = "diam") %>%
  select(rep, cluster, fruit, meas, diam, persist) -> diam
```

Dates were then added to the data frame.

```{r, warning=FALSE}
diam %>%
  mutate(date = case_when(meas == "meas1" ~ ymd(20210428),
                          meas == "meas2" ~ ymd(20210501),
                          meas == "meas3" ~ ymd(20210505),
                          meas == "meas4" ~ ymd(20210507),
                          meas == "meas5" ~ ymd(20210509),
                          meas == "meas6" ~ ymd(20210511),
                          meas == "meas7" ~ ymd(20210514))) -> diam
```

The file then writes a .csv file for all NIR and diameter data