---
title: 'NIR FGM Model Building'
author: "Jimmy Larson"
date: "10/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, error = FALSE, message = FALSE, include = FALSE}
# load packages----
library(tidyverse)
library(xgboost)
## set seed----
set.seed(123)
## read in data----
meas1 <- read_csv("data/2021/honeycrisp/model_building/meas1_spectra.csv")
meas1Smoted <- read_csv("data/2021/honeycrisp/model_building/meas1Smoted.csv")
meas2 <- read_csv("data/2021/honeycrisp/model_building/meas2_spectra.csv")
meas2Smoted <- read_csv("data/2021/honeycrisp/model_building/meas2Smoted.csv")
meas3 <- read_csv("data/2021/honeycrisp/model_building/meas3_spectra.csv")
meas3Smoted <- read_csv("data/2021/honeycrisp/model_building/meas3Smoted.csv")
meas4 <- read_csv("data/2021/honeycrisp/model_building/meas4_spectra.csv")
meas4Smoted <- read_csv("data/2021/honeycrisp/model_building/meas4Smoted.csv")
meas5 <- read_csv("data/2021/honeycrisp/model_building/meas5_spectra.csv")
meas5Smoted <- read_csv("data/2021/honeycrisp/model_building/meas5Smoted.csv")
meas6 <- read_csv("data/2021/honeycrisp/model_building/meas6_spectra.csv")
meas6Smoted <- read_csv("data/2021/honeycrisp/model_building/meas6Smoted.csv")
meas7 <- read_csv("data/2021/honeycrisp/model_building/meas7_spectra.csv")
meas7Smoted <- read_csv("data/2021/honeycrisp/model_building/meas7Smoted.csv")
diff1 <- read_csv("data/2021/honeycrisp/model_building/diff1_spectra.csv")
diff1Smoted <- read_csv("data/2021/honeycrisp/model_building/diff1Smoted.csv")
diff2 <- read_csv("data/2021/honeycrisp/model_building/diff2_spectra.csv")
diff2Smoted <- read_csv("data/2021/honeycrisp/model_building/diff2Smoted.csv")
diff3 <- read_csv("data/2021/honeycrisp/model_building/diff3_spectra.csv")
diff3Smoted <- read_csv("data/2021/honeycrisp/model_building/diff3Smoted.csv")
diff4 <- read_csv("data/2021/honeycrisp/model_building/diff4_spectra.csv")
diff4Smoted <- read_csv("data/2021/honeycrisp/model_building/diff4Smoted.csv")
diff5 <- read_csv("data/2021/honeycrisp/model_building/diff5_spectra.csv")
diff5Smoted <- read_csv("data/2021/honeycrisp/model_building/diff5Smoted.csv")
diff6 <- read_csv("data/2021/honeycrisp/model_building/diff6_spectra.csv")
diff6Smoted <- read_csv("data/2021/honeycrisp/model_building/diff6Smoted.csv")
## build XGBoost model for ind. dates----
### meas1
meas1 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> meas1
meas1Cases <- as.data.frame(table(meas1$persistCode))
meas1Per <- meas1Cases[1,2]
meas1Abs <- meas1Cases[2,2]
meas1 <- data.matrix(meas1)
xgbMeas1data <- xgb.DMatrix(meas1[,-1], label = meas1[,1])
xgbMeas1 <- xgb.cv(data = xgbMeas1data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas1Abs/meas1Per,
                   max_depth = 4, 
                   eta = .3,
                   prediction = TRUE,
                   objective = "binary:logistic")
### meas2
meas2 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> meas2
meas2Cases <- as.data.frame(table(meas2$persistCode))
meas2Per <- meas2Cases[1,2]
meas2Abs <- meas2Cases[2,2]
meas2 <- data.matrix(meas2)
xgbMeas2data <- xgb.DMatrix(meas2[,-1], label = meas2[,1])
xgbMeas2 <- xgb.cv(data = xgbMeas2data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas2Abs/meas2Per,
                   max_depth = 4, 
                   eta = .3,
                   objective = "binary:logistic")
### meas3
meas3 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> meas3
meas3Cases <- as.data.frame(table(meas3$persistCode))
meas3Per <- meas3Cases[1,2]
meas3Abs <- meas3Cases[2,2]
meas3 <- data.matrix(meas3)
xgbMeas3data <- xgb.DMatrix(meas3[,-1], label = meas3[,1])
xgbMeas3cv <- xgb.cv(data = xgbMeas3data,
                     nround=3,
                     nfold = 5,
                     metrics = list("error","rmse","auc"),
                     scale_pos_weight = meas3Abs/meas3Per,
                     max_depth = 4, 
                     eta = .3,
                     objective = "binary:logistic")
### meas4   
meas4 %>%
  drop_na() %>%
  select(persistCode, 6:311)-> meas4
meas4Cases <- as.data.frame(table(meas4$persistCode))
meas4Per <- meas4Cases[1,2]
meas4Abs <- meas4Cases[2,2]
meas4 <- data.matrix(meas4)
xgbMeas4data <- xgb.DMatrix(meas4[,-1], label = meas4[,1])
xgbMeas4 <- xgb.cv(data = xgbMeas4data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas4Abs/meas4Per,
                   max_depth = 4, 
                   eta = .3,
                   objective = "binary:logistic")
### meas5
meas5 %>%
  drop_na() %>%
  select(persistCode, 6:311)-> meas5
meas5Cases <- as.data.frame(table(meas5$persistCode))
meas5Per <- meas5Cases[1,2]
meas5Abs <- meas5Cases[2,2]
meas5 <- data.matrix(meas5)
xgbMeas5data <- xgb.DMatrix(meas5[,-1], label = meas5[,1])
xgbMeas5 <- xgb.cv(data = xgbMeas5data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas5Per/meas5Abs,
                   max_depth = 4, 
                   eta = .3,
                   objective = "binary:logistic")
### meas6
meas6 %>%
  drop_na() %>%
  select(persistCode, 6:311)-> meas6
meas6Cases <- as.data.frame(table(meas6$persistCode))
meas6Per <- meas6Cases[1,2]
meas6Abs <- meas6Cases[2,2]
meas6 <- data.matrix(meas6)
xgbMeas6data <- xgb.DMatrix(meas6[,-1], label = meas6[,1])
xgbMeas6 <- xgb.cv(data = xgbMeas6data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas6Abs/meas6Per,
                   max_depth = 4, 
                   eta = .3,
                   objective = "binary:logistic")
### meas7
meas7 %>%
  drop_na() %>%
  select(persistCode, 6:311)-> meas7
meas7Cases <- as.data.frame(table(meas7$persistCode))
meas7Per <- meas7Cases[1,2]
meas7Abs <- meas7Cases[2,2]
meas7 <- data.matrix(meas7)
xgbMeas7data <- xgb.DMatrix(meas7[,-1], label = meas7[,1])
xgbMeas7 <- xgb.cv(data = xgbMeas7data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas7Abs/meas7Per,
                   max_depth = 4, 
                   eta = .3,
                   objective = "binary:logistic")
## build XGBoost for ind. dates with SMOTE----
### meas1
meas1SmotedMatrix <- data.matrix(meas1Smoted)
xgbMeas1Smoted <- xgb.DMatrix(meas1SmotedMatrix[,-1], label = meas1SmotedMatrix[,1])
xgbMeas1SmotedCv <- xgb.cv(data = xgbMeas1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas2
meas2SmotedMatrix <- data.matrix(meas2Smoted)
xgbMeas2Smoted <- xgb.DMatrix(meas2SmotedMatrix[,-1], label = meas2SmotedMatrix[,1])
xgbMeas2SmotedCv <- xgb.cv(data = xgbMeas2Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas3
meas3SmotedMatrix <- data.matrix(meas3Smoted)
xgbMeas3Smoted <- xgb.DMatrix(meas3SmotedMatrix[,-1], label = meas3SmotedMatrix[,1])
xgbMeas3SmotedCv <- xgb.cv(data = xgbMeas3Smoted,
                          nfold = 5,
                          nrounds = 3,
                          max_depth = 4,
                          eta = .3,
                          objective = "binary:logistic",
                          prediction = TRUE,
                          metrics = list("error","rmse","auc"))
### meas4
meas4SmotedMatrix <- data.matrix(meas4Smoted)
xgbmeas4Smoted <- xgb.DMatrix(meas4SmotedMatrix[,-1], label = meas4SmotedMatrix[,1])
xgbmeas4SmotedCv <- xgb.cv(data = xgbmeas4Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas5
meas5SmotedMatrix <- data.matrix(meas5Smoted)
xgbmeas5Smoted <- xgb.DMatrix(meas5SmotedMatrix[,-1], label = meas5SmotedMatrix[,1])
xgbmeas5SmotedCv <- xgb.cv(data = xgbmeas5Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas6
meas6SmotedMatrix <- data.matrix(meas6Smoted)
xgbmeas6Smoted <- xgb.DMatrix(meas6SmotedMatrix[,-1], label = meas6SmotedMatrix[,1])
xgbmeas6SmotedCv <- xgb.cv(data = xgbmeas6Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas7
meas7SmotedMatrix <- data.matrix(meas7Smoted)
xgbmeas7Smoted <- xgb.DMatrix(meas7SmotedMatrix[,-1], label = meas7SmotedMatrix[,1])
xgbmeas7SmotedCv <- xgb.cv(data = xgbmeas7Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
## XGBoost for differences in dates----
### diff1
diff1 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff1
diff1Cases <- as.data.frame(table(diff1$persistCode))
diff1Per <- diff1Cases[1,2]
diff1Abs <- diff1Cases[2,2]
diff1Matrix <- data.matrix(diff1)
xgbDiff1Data <- xgb.DMatrix(diff1Matrix[,-1], label= diff1Matrix[,1])
xgbDiff1Cv <- xgb.cv(data = xgbDiff1Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff1Abs/diff1Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
### diff2
diff2 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff2
diff2Cases <- as.data.frame(table(diff2$persistCode))
diff2Per <- diff2Cases[1,2]
diff2Abs <- diff2Cases[2,2]
diff2Matrix <- data.matrix(diff2)
xgbdiff2Data <- xgb.DMatrix(diff2Matrix[,-1], label= diff2Matrix[,1])
xgbdiff2Cv <- xgb.cv(data = xgbdiff2Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff2Abs/diff2Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
### diff3
diff3 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff3
diff3Cases <- as.data.frame(table(diff3$persistCode))
diff3Per <- diff3Cases[1,2]
diff3Abs <- diff3Cases[2,2]
diff3Matrix <- data.matrix(diff3)
xgbdiff3Data <- xgb.DMatrix(diff3Matrix[,-1], label= diff3Matrix[,1])
xgbdiff3Cv <- xgb.cv(data = xgbdiff3Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff3Abs/diff3Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
### diff4
diff4 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff4
diff4Cases <- as.data.frame(table(diff4$persistCode))
diff4Per <- diff4Cases[1,2]
diff4Abs <- diff4Cases[2,2]
diff4Matrix <- data.matrix(diff4)
xgbdiff4Data <- xgb.DMatrix(diff4Matrix[,-1], label= diff4Matrix[,1])
xgbdiff4Cv <- xgb.cv(data = xgbdiff4Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff4Abs/diff4Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
### diff5
diff5 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff5
diff5Cases <- as.data.frame(table(diff5$persistCode))
diff5Per <- diff5Cases[1,2]
diff5Abs <- diff5Cases[2,2]
diff5Matrix <- data.matrix(diff5)
xgbdiff5Data <- xgb.DMatrix(diff5Matrix[,-1], label= diff5Matrix[,1])
xgbdiff5Cv <- xgb.cv(data = xgbdiff5Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff5Abs/diff5Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
### diff6
diff6 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff6
diff6Cases <- as.data.frame(table(diff6$persistCode))
diff6Per <- diff6Cases[1,2]
diff6Abs <- diff6Cases[2,2]
diff6Matrix <- data.matrix(diff6)
xgbdiff6Data <- xgb.DMatrix(diff6Matrix[,-1], label= diff6Matrix[,1])
xgbdiff6Cv <- xgb.cv(data = xgbdiff6Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff6Abs/diff6Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
## XGBoost for diff with SMOTE----
### diff1
diff1SmotedMatrix <- data.matrix(diff1Smoted)
xgbdiff1Smoted <- xgb.DMatrix(diff1SmotedMatrix[,-1], label = diff1SmotedMatrix[,1])
xgbdiff1SmotedCv <- xgb.cv(data = xgbdiff1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### diff2
diff2SmotedMatrix <- data.matrix(diff2Smoted)
xgbdiff2Smoted <- xgb.DMatrix(diff2SmotedMatrix[,-1], label = diff2SmotedMatrix[,1])
xgbdiff2SmotedCv <- xgb.cv(data = xgbdiff2Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### diff3
diff3SmotedMatrix <- data.matrix(diff3Smoted)
xgbdiff3Smoted <- xgb.DMatrix(diff3SmotedMatrix[,-1], label = diff3SmotedMatrix[,1])
xgbdiff3SmotedCv <- xgb.cv(data = xgbdiff3Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### diff4
diff4SmotedMatrix <- data.matrix(diff4Smoted)
xgbdiff4Smoted <- xgb.DMatrix(diff4SmotedMatrix[,-1], label = diff4SmotedMatrix[,1])
xgbdiff4SmotedCv <- xgb.cv(data = xgbdiff4Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### diff5
diff5SmotedMatrix <- data.matrix(diff5Smoted)
xgbdiff5Smoted <- xgb.DMatrix(diff5SmotedMatrix[,-1], label = diff5SmotedMatrix[,1])
xgbdiff5SmotedCv <- xgb.cv(data = xgbdiff5Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### diff6
diff6SmotedMatrix <- data.matrix(diff6Smoted)
xgbdiff6Smoted <- xgb.DMatrix(diff6SmotedMatrix[,-1], label = diff6SmotedMatrix[,1])
xgbdiff6SmotedCv <- xgb.cv(data = xgbdiff6Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
## XGBoost variable importance for ind. dates with SMOTE----
### meas1
xgbMeas1SmotedTrain <- xgb.train(data = xgbMeas1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic")
xgbMeas1SmotedImp <- xgb.importance(feature_names = colnames(meas1Smoted[,-1]), model = xgbMeas1SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas1SmotedImp[1:20])
xgbMeas1SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas1SmotedImpFeat
xgbMeas1SmotedSelectedFeat <- xgbMeas1SmotedImpFeat$Feature
meas1Smoted %>%
  select(`meas1Smote$Y`, xgbMeas1SmotedSelectedFeat) %>%
  data.matrix() -> meas1SmotedSelectedMatrix
xgbMeas1SmotedSelected <- xgb.DMatrix(meas1SmotedSelectedMatrix[,-1], label = meas1SmotedSelectedMatrix[,1])
xgbMeas1SmotedSelectedCv <- xgb.cv(data = xgbMeas1SmotedSelected,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
### meas2
xgbMeas2SmotedTrain <- xgb.train(data = xgbMeas2Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas2SmotedImp <- xgb.importance(feature_names = colnames(meas2Smoted[,-1]), model = xgbMeas2SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas2SmotedImp[1:20])
xgbMeas2SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas2SmotedImpFeat
xgbMeas2SmotedSelectedFeat <- xgbMeas2SmotedImpFeat$Feature
meas2Smoted %>%
  select(`meas2Smote$Y`, xgbMeas2SmotedSelectedFeat) %>%
  data.matrix() -> meas2SmotedSelectedMatrix
xgbMeas2SmotedSelected <- xgb.DMatrix(meas2SmotedSelectedMatrix[,-1], label = meas2SmotedSelectedMatrix[,1])
xgbMeas2SmotedSelectedCv <- xgb.cv(data = xgbMeas2SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### meas3
xgbMeas3SmotedTrain <- xgb.train(data = xgbMeas3Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas3SmotedImp <- xgb.importance(feature_names = colnames(meas3Smoted[,-1]), model = xgbMeas3SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas3SmotedImp[1:20])
xgbMeas3SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas3SmotedImpFeat
xgbMeas3SmotedSelectedFeat <- xgbMeas3SmotedImpFeat$Feature
meas3Smoted %>%
  select(`meas3Smote$Y`, xgbMeas3SmotedSelectedFeat) %>%
  data.matrix() -> meas3SmotedSelectedMatrix
xgbMeas3SmotedSelected <- xgb.DMatrix(meas3SmotedSelectedMatrix[,-1], label = meas3SmotedSelectedMatrix[,1])
xgbMeas3SmotedSelectedCv <- xgb.cv(data = xgbMeas3SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### meas4
xgbMeas4SmotedTrain <- xgb.train(data = xgbmeas4Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas4SmotedImp <- xgb.importance(feature_names = colnames(meas4Smoted[,-1]), model = xgbMeas4SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas4SmotedImp[1:20])
xgbMeas4SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas4SmotedImpFeat
xgbMeas4SmotedSelectedFeat <- xgbMeas4SmotedImpFeat$Feature
meas4Smoted %>%
  select(`meas4Smote$Y`, xgbMeas4SmotedSelectedFeat) %>%
  data.matrix() -> meas4SmotedSelectedMatrix
xgbMeas4SmotedSelected <- xgb.DMatrix(meas4SmotedSelectedMatrix[,-1], label = meas4SmotedSelectedMatrix[,1])
xgbMeas4SmotedSelectedCv <- xgb.cv(data = xgbMeas4SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### meas5
xgbMeas5SmotedTrain <- xgb.train(data = xgbmeas5Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas5SmotedImp <- xgb.importance(feature_names = colnames(meas5Smoted[,-1]), model = xgbMeas5SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas5SmotedImp[1:20])
xgbMeas5SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas5SmotedImpFeat
xgbMeas5SmotedSelectedFeat <- xgbMeas5SmotedImpFeat$Feature
meas5Smoted %>%
  select(`meas5Smote$Y`, xgbMeas5SmotedSelectedFeat) %>%
  data.matrix() -> meas5SmotedSelectedMatrix
xgbMeas5SmotedSelected <- xgb.DMatrix(meas5SmotedSelectedMatrix[,-1], label = meas5SmotedSelectedMatrix[,1])
xgbMeas5SmotedSelectedCv <- xgb.cv(data = xgbMeas5SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### meas6
xgbMeas6SmotedTrain <- xgb.train(data = xgbmeas6Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas6SmotedImp <- xgb.importance(feature_names = colnames(meas6Smoted[,-1]), model = xgbMeas6SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas6SmotedImp[1:20])
xgbMeas6SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas6SmotedImpFeat
xgbMeas6SmotedSelectedFeat <- xgbMeas6SmotedImpFeat$Feature
meas6Smoted %>%
  select(`meas6Smote$Y`, xgbMeas6SmotedSelectedFeat) %>%
  data.matrix() -> meas6SmotedSelectedMatrix
xgbMeas6SmotedSelected <- xgb.DMatrix(meas6SmotedSelectedMatrix[,-1], label = meas6SmotedSelectedMatrix[,1])
xgbMeas6SmotedSelectedCv <- xgb.cv(data = xgbMeas6SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### meas7
xgbMeas7SmotedTrain <- xgb.train(data = xgbmeas7Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbMeas7SmotedImp <- xgb.importance(feature_names = colnames(meas7Smoted[,-1]), model = xgbMeas7SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas7SmotedImp[1:20])
xgbMeas7SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas7SmotedImpFeat
xgbMeas7SmotedSelectedFeat <- xgbMeas7SmotedImpFeat$Feature
meas7Smoted %>%
  select(`meas7Smote$Y`, xgbMeas7SmotedSelectedFeat) %>%
  data.matrix() -> meas7SmotedSelectedMatrix
xgbMeas7SmotedSelected <- xgb.DMatrix(meas7SmotedSelectedMatrix[,-1], label = meas7SmotedSelectedMatrix[,1])
xgbMeas7SmotedSelectedCv <- xgb.cv(data = xgbMeas7SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))

## XGBoost variable importance for differences in dates with SMOTE----
### diff1
xgbDiff1SmotedTrain <- xgb.train(data = xgbdiff1Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff1SmotedImp <- xgb.importance(feature_names = colnames(diff1Smoted[,-1]), model = xgbDiff1SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff1SmotedImp[1:20])
xgbDiff1SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff1SmotedImpFeat
xgbDiff1SmotedSelectedFeat <- xgbDiff1SmotedImpFeat$Feature
diff1Smoted %>%
  select(`diff1Smote$Y`, xgbDiff1SmotedSelectedFeat) %>%
  data.matrix() -> diff1SmotedSelectedMatrix
xgbDiff1SmotedSelected <- xgb.DMatrix(diff1SmotedSelectedMatrix[,-1], label = diff1SmotedSelectedMatrix[,1])
xgbDiff1SmotedSelectedCv <- xgb.cv(data = xgbDiff1SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### diff2
xgbDiff2SmotedTrain <- xgb.train(data = xgbdiff2Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff2SmotedImp <- xgb.importance(feature_names = colnames(diff2Smoted[,-1]), model = xgbDiff2SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff2SmotedImp[1:20])
xgbDiff2SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff2SmotedImpFeat
xgbDiff2SmotedSelectedFeat <- xgbDiff2SmotedImpFeat$Feature
diff2Smoted %>%
  select(`diff2Smote$Y`, xgbDiff2SmotedSelectedFeat) %>%
  data.matrix() -> diff2SmotedSelectedMatrix
xgbDiff2SmotedSelected <- xgb.DMatrix(diff2SmotedSelectedMatrix[,-1], label = diff2SmotedSelectedMatrix[,1])
xgbDiff2SmotedSelectedCv <- xgb.cv(data = xgbDiff2SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### diff3
xgbDiff3SmotedTrain <- xgb.train(data = xgbdiff3Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff3SmotedImp <- xgb.importance(feature_names = colnames(diff3Smoted[,-1]), model = xgbDiff3SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff3SmotedImp[1:20])
xgbDiff3SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff3SmotedImpFeat
xgbDiff3SmotedSelectedFeat <- xgbDiff3SmotedImpFeat$Feature
diff3Smoted %>%
  select(`diff3Smote$Y`, xgbDiff3SmotedSelectedFeat) %>%
  data.matrix() -> diff3SmotedSelectedMatrix
xgbDiff3SmotedSelected <- xgb.DMatrix(diff3SmotedSelectedMatrix[,-1], label = diff3SmotedSelectedMatrix[,1])
xgbDiff3SmotedSelectedCv <- xgb.cv(data = xgbDiff3SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### diff4
xgbDiff4SmotedTrain <- xgb.train(data = xgbdiff4Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff4SmotedImp <- xgb.importance(feature_names = colnames(diff4Smoted[,-1]), model = xgbDiff4SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff4SmotedImp[1:20])
xgbDiff4SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff4SmotedImpFeat
xgbDiff4SmotedSelectedFeat <- xgbDiff4SmotedImpFeat$Feature
diff4Smoted %>%
  select(`diff4Smote$Y`, xgbDiff4SmotedSelectedFeat) %>%
  data.matrix() -> diff4SmotedSelectedMatrix
xgbDiff4SmotedSelected <- xgb.DMatrix(diff4SmotedSelectedMatrix[,-1], label = diff4SmotedSelectedMatrix[,1])
xgbDiff4SmotedSelectedCv <- xgb.cv(data = xgbDiff4SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### diff5
xgbDiff5SmotedTrain <- xgb.train(data = xgbdiff5Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff5SmotedImp <- xgb.importance(feature_names = colnames(diff5Smoted[,-1]), model = xgbDiff5SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff5SmotedImp[1:20])
xgbDiff5SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff5SmotedImpFeat
xgbDiff5SmotedSelectedFeat <- xgbDiff5SmotedImpFeat$Feature
diff5Smoted %>%
  select(`diff5Smote$Y`, xgbDiff5SmotedSelectedFeat) %>%
  data.matrix() -> diff5SmotedSelectedMatrix
xgbDiff5SmotedSelected <- xgb.DMatrix(diff5SmotedSelectedMatrix[,-1], label = diff5SmotedSelectedMatrix[,1])
xgbDiff5SmotedSelectedCv <- xgb.cv(data = xgbDiff5SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
### diff6
xgbDiff6SmotedTrain <- xgb.train(data = xgbdiff6Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff6SmotedImp <- xgb.importance(feature_names = colnames(diff6Smoted[,-1]), model = xgbDiff6SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff6SmotedImp[1:20])
xgbDiff6SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff6SmotedImpFeat
xgbDiff6SmotedSelectedFeat <- xgbDiff6SmotedImpFeat$Feature
diff6Smoted %>%
  select(`diff6Smote$Y`, xgbDiff6SmotedSelectedFeat) %>%
  data.matrix() -> diff6SmotedSelectedMatrix
xgbDiff6SmotedSelected <- xgb.DMatrix(diff6SmotedSelectedMatrix[,-1], label = diff6SmotedSelectedMatrix[,1])
xgbDiff6SmotedSelectedCv <- xgb.cv(data = xgbDiff6SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))

```

## Introduction

This file describes the process for building a model for predicting fruitlet abscission rates following a chemical thinner application from Visible/Near Infrared Spectroscopy (NIR) data that was collected in the spring of 2021 in Henderson County, NC. On the cultivar 'Honeycrisp' 20 spurs on five trees were tagged, each fruit had their NIR spectra and diameter measured surrounding a chemical thinner application. The thinner application was made on May 2 and final fruit final fruitlet persistence was determined on June 16th. NIR and dimaeter data was collected on:

* April 28 (Measurement 1)

* May 1 (Measurement 2)

* May 5 (Measurement 3)

* May 7 (Measurement 4)

* May 9 (Measurement 5)

* May 11 (Measurement 6)

* May 14 (Measurement 7)

Three different classification models - Logisitic Regression, Random Forest and XGBoost - were tested against the widely available Fruit Growth Model (FGM) that utilizes fruitlet diameter to predict fruitlet abscission. See "FGM_model_test_notes.Rmd" for specifics on FGM model performance. Due to the majority of fruit abscising following the thinner application, Synthetic Minority Oversampling Technique (SMOTE) was tested to determine model performance from balancing the dataset, see "Smote_notes.Rmd" for more information on balancing data with SMOTE. Individual measurement dates and well as the difference in fruitlet absorption between successive dates were compared as well for model building. Where applicable, models were also tested with selected variables.

Each model was built in a separate R scripts - "NIR_PLS_model.R", "NIR_RF_model.R", and "NIR_XGBoost_model.R". For all models, the seed was set at 123:

```{r, eval=FALSE, warning=FALSE}
set.seed(123)
```

For all models, absorbance spectra at each wavelength (310-1100nm, every 3nm - 306 total) or selected wavelengths were used as predictor variables, while the response variable was a binary outcome - 'persistCode' - where a 0 was assigned to fruit that eventually abscised and a 1 was assigned to fruit that had persisted folliwing a final fruit set determination that was done follwing the drop period.

## Partial Least Squares Regression

## Random Forests

## XGBoost

Below describes the process for building a model for each single measurement date (total of 7) and differences in spectra between consecutive measurement dates (total of 6) with and without SMOTE. Then, due to SMOTE outperforming the unbalanced dataset, those datasets were used to test model performance with selected wavelengths.

A dataset was load for single date and difference spectra, with and without SMOTE...

```{r, eval=FALSE, warning=FALSE}
meas1 <- read_csv("data/2021/honeycrisp/model_building/meas1_spectra.csv")
meas1Smoted <- read_csv("data/2021/honeycrisp/model_building/meas1Smoted.csv")
diff1 <- read_csv("data/2021/honeycrisp/model_building/diff1_spectra.csv")
diff1Smoted <- read_csv("data/2021/honeycrisp/model_building/diff1Smoted.csv")
```

### Single Measurement Dates 

For unblanced single measurement data, missing values were removed and the predictor and response variables were selected...

```{r, eval=FALSE, warning=FALSE}
meas1 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> meas1
```

Then, to assign a weighted value for the rare case of a persisted fruitlet the number of persisted and abscised fruit were determined. The ratio of abscised to persisted fruit were used in the "scale_pos_weight" argument in the model. 

```{r, eval=FALSE, warning=FALSE}
meas1Cases <- as.data.frame(table(meas1$persistCode))
meas1Per <- meas1Cases[1,2]
meas1Abs <- meas1Cases[2,2]
```

Data had to then be prepared for xgboost model by converting to a matrix and then to a matrix of class xgb.DMatrix. xgb.DMatrix first takes the predictor variables and then specifies the response as the label.

```{r, eval=FALSE, warning=FALSE}
meas1 <- data.matrix(meas1)
xgbMeas1data <- xgb.DMatrix(meas1[,-1], label = meas1[,1])
```

Using the xgb.Dmatrix, an XGBoost model is then built. Because this is a classification problem, a "binary:logistic" model was chosen. This model was 5 fold cross validated and 3 iterations of the model were built. These parameters will be used in all successive XGBoost models.

```{r, eval=FALSE, warning=FALSE}
xgbMeas1 <- xgb.cv(data = xgbMeas1data,
                   nround=3,
                   nfold = 5,
                   metrics = list("error","rmse","auc"),
                   scale_pos_weight = meas1Abs/meas1Per,
                   max_depth = 4, 
                   eta = .3,
                   prediction = TRUE,
                   objective = "binary:logistic")
```

### Single Measurement Dates Balanced with SMOTE

Since SMOTE balances data, we do not need to first calculate the ratio of abscised to persisted fruit and can go into changing the class of data and running the model.

```{r, eval=FALSE, warning=FALSE}
meas1SmotedMatrix <- data.matrix(meas1Smoted)
xgbMeas1Smoted <- xgb.DMatrix(meas1SmotedMatrix[,-1], label = meas1SmotedMatrix[,1])
xgbMeas1SmotedCv <- xgb.cv(data = xgbMeas1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
```

### Difference in Spectra

The unbalanced difference in spectra model follows the same process as the single measurement date above...

```{r, eval=FALSE, warning=FALSE}
diff1 %>%
  drop_na() %>%
  select(persistCode, 6:311) -> diff1
diff1Cases <- as.data.frame(table(diff1$persistCode))
diff1Per <- diff1Cases[1,2]
diff1Abs <- diff1Cases[2,2]
diff1Matrix <- data.matrix(diff1)
xgbDiff1Data <- xgb.DMatrix(diff1Matrix[,-1], label= diff1Matrix[,1])
xgbDiff1Cv <- xgb.cv(data = xgbDiff1Data,
                     nfold = 5,
                     nrounds = 3,
                     scale_pos_weight = diff1Abs/diff1Per,
                     max_depth = 4,
                     eta = .3,
                     objective = "binary:logistic",
                     prediction = TRUE,
                     metrics = list("error", "rmse", "auc"))
```

### Difference in Spectra Balanced with SMOTE

As with the unblanced difference spectra model, the SMOTE balanced model building steps are the same as the single measurement dates

```{r, eval=FALSE, warning=FALSE}
diff1SmotedMatrix <- data.matrix(diff1Smoted)
xgbdiff1Smoted <- xgb.DMatrix(diff1SmotedMatrix[,-1], label = diff1SmotedMatrix[,1])
xgbdiff1SmotedCv <- xgb.cv(data = xgbdiff1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
```

### Selected Wavelengths on Single Measurement Dates

To build a model with the most important wavelengths, a model is built from the full dataset, using xgb.train and the same parameters as the XGBoost models above.

```{r, eval=FALSE, warning=FALSE}
xgbMeas1SmotedTrain <- xgb.train(data = xgbMeas1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic")
```

A matrix with each variables 'gain' - how much it contributes to the model - is returned from the xgb.importance function.

```{r, warning=FALSE}
xgbMeas1SmotedTrain <- xgb.train(data = xgbMeas1Smoted,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic")
xgbMeas1SmotedImp <- xgb.importance(feature_names = colnames(meas1Smoted[,-1]), model = xgbMeas1SmotedTrain)
xgb.plot.importance(importance_matrix = xgbMeas1SmotedImp[1:20])
```

From the plot of the 20 most important features, a cut off of 0.025 was chosen for the selected model.

```{r, eval=FALSE, warning=FALSE}
xgbMeas1SmotedImp %>%
  filter(Gain >= 0.025) -> xgbMeas1SmotedImpFeat
```

These are then selected from the original dataset

```{r, eval=FALSE, warning=FALSE}
xgbMeas1SmotedSelectedFeat <- xgbMeas1SmotedImpFeat$Feature
meas1Smoted %>%
  select(`meas1Smote$Y`, xgbMeas1SmotedSelectedFeat) %>%
  data.matrix() -> meas1SmotedSelectedMatrix
```

This model is then built using cross validation, as above.

```{r, eval=FALSE, warning=FALSE}
xgbMeas1SmotedSelected <- xgb.DMatrix(meas1SmotedSelectedMatrix[,-1], label = meas1SmotedSelectedMatrix[,1])
xgbMeas1SmotedSelectedCv <- xgb.cv(data = xgbMeas1SmotedSelected,
                           nfold = 5,
                           nrounds = 3,
                           max_depth = 4,
                           eta = .3,
                           objective = "binary:logistic",
                           prediction = TRUE,
                           metrics = list("error","rmse","auc"))
```

### Selected Wavelengths on Difference between Dates

A selected wavelengths model for differences in absorption was built using the same process.

```{r, eval=FALSE, warning=FALSE}
xgbDiff1SmotedTrain <- xgb.train(data = xgbdiff1Smoted,
                                 nfold = 5,
                                 nrounds = 3,
                                 max_depth = 4,
                                 eta = .3,
                                 objective = "binary:logistic")
xgbDiff1SmotedImp <- xgb.importance(feature_names = colnames(diff1Smoted[,-1]), model = xgbDiff1SmotedTrain)
xgb.plot.importance(importance_matrix = xgbDiff1SmotedImp[1:20])
xgbDiff1SmotedImp %>%
  filter(Gain >= 0.025) -> xgbDiff1SmotedImpFeat
xgbDiff1SmotedSelectedFeat <- xgbDiff1SmotedImpFeat$Feature
diff1Smoted %>%
  select(`diff1Smote$Y`, xgbDiff1SmotedSelectedFeat) %>%
  data.matrix() -> diff1SmotedSelectedMatrix
xgbDiff1SmotedSelected <- xgb.DMatrix(diff1SmotedSelectedMatrix[,-1], label = diff1SmotedSelectedMatrix[,1])
xgbDiff1SmotedSelectedCv <- xgb.cv(data = xgbDiff1SmotedSelected,
                                   nfold = 5,
                                   nrounds = 3,
                                   max_depth = 4,
                                   eta = .3,
                                   objective = "binary:logistic",
                                   prediction = TRUE,
                                   metrics = list("error","rmse","auc"))
```

### Comparison of XGBoost Models

```{r, warning=FALSE, echo=FALSE}
library(knitr)
xgb.metrics <- data.frame("Days after Thinner" = c(-4, -1, 3, 5, 7, 9, 12),
                          "Single Date Error" = c(xgbMeas1$evaluation_log$test_error_mean[3],
                                                  xgbMeas2$evaluation_log$test_error_mean[3],
                                                  xgbMeas3cv$evaluation_log$test_error_mean[3],
                                                  xgbMeas4$evaluation_log$test_error_mean[3],
                                                  xgbMeas5$evaluation_log$test_error_mean[3],
                                                  xgbMeas6$evaluation_log$test_error_mean[3],
                                                  xgbMeas7$evaluation_log$test_error_mean[3]),
                          "Single Date SMOTE Error" = c(xgbMeas1SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbMeas2SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbMeas3SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbmeas4SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbmeas5SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbmeas6SmotedCv$evaluation_log$test_error_mean[3],
                                                        xgbmeas7SmotedCv$evaluation_log$test_error_mean[3]),
                          "Diff. Between Dates Error"  = c(NA,
                                                           xgbDiff1Cv$evaluation_log$test_error_mean[3],
                                                           xgbdiff2Cv$evaluation_log$test_error_mean[3],
                                                           xgbdiff3Cv$evaluation_log$test_error_mean[3],
                                                           xgbdiff4Cv$evaluation_log$test_error_mean[3],
                                                           xgbdiff5Cv$evaluation_log$test_error_mean[3],
                                                           xgbdiff6Cv$evaluation_log$test_error_mean[3]),
                          "Diff. Between Dates SMOTE Error"  = c(NA,
                                                                 xgbdiff1SmotedCv$evaluation_log$test_error_mean[3],
                                                                 xgbdiff2SmotedCv$evaluation_log$test_error_mean[3],
                                                                 xgbdiff3SmotedCv$evaluation_log$test_error_mean[3],
                                                                 xgbdiff4SmotedCv$evaluation_log$test_error_mean[3],
                                                                 xgbdiff5SmotedCv$evaluation_log$test_error_mean[3],
                                                                 xgbdiff6SmotedCv$evaluation_log$test_error_mean[3]),
                          "Single Date Selected Error" = c(xgbMeas1SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas2SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas3SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas4SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas5SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas6SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                           xgbMeas7SmotedSelectedCv$evaluation_log$test_error_mean[3]),
                          "Diff. Between Dates Selected Error" = c(NA,
                                                                   xgbDiff1SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                                   xgbDiff2SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                                   xgbDiff3SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                                   xgbDiff4SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                                   xgbDiff5SmotedSelectedCv$evaluation_log$test_error_mean[3],
                                                                   xgbDiff6SmotedSelectedCv$evaluation_log$test_error_mean[3]),
                          "Single Date AUC" = c(xgbMeas1$evaluation_log$test_auc_mean[3],
                                                xgbMeas2$evaluation_log$test_auc_mean[3],
                                                xgbMeas3cv$evaluation_log$test_auc_mean[3],
                                                xgbMeas4$evaluation_log$test_auc_mean[3],
                                                xgbMeas5$evaluation_log$test_auc_mean[3],
                                                xgbMeas6$evaluation_log$test_auc_mean[3],
                                                xgbMeas7$evaluation_log$test_auc_mean[3]),
                          "Single Date SMOTE AUC" = c(xgbMeas1SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbMeas2SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbMeas3SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbmeas4SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbmeas5SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbmeas6SmotedCv$evaluation_log$test_auc_mean[3],
                                                        xgbmeas7SmotedCv$evaluation_log$test_auc_mean[3]),
                          "Diff. Between Dates AUC"  = c(NA,
                                                           xgbDiff1Cv$evaluation_log$test_auc_mean[3],
                                                           xgbdiff2Cv$evaluation_log$test_auc_mean[3],
                                                           xgbdiff3Cv$evaluation_log$test_auc_mean[3],
                                                           xgbdiff4Cv$evaluation_log$test_auc_mean[3],
                                                           xgbdiff5Cv$evaluation_log$test_auc_mean[3],
                                                           xgbdiff6Cv$evaluation_log$test_auc_mean[3]),
                          "Diff. Between Dates SMOTE AUC"  = c(NA,
                                                                 xgbdiff1SmotedCv$evaluation_log$test_auc_mean[3],
                                                                 xgbdiff2SmotedCv$evaluation_log$test_auc_mean[3],
                                                                 xgbdiff3SmotedCv$evaluation_log$test_auc_mean[3],
                                                                 xgbdiff4SmotedCv$evaluation_log$test_auc_mean[3],
                                                                 xgbdiff5SmotedCv$evaluation_log$test_auc_mean[3],
                                                                 xgbdiff6SmotedCv$evaluation_log$test_auc_mean[3]),
                          "Single Date Selected AUC" = c(xgbMeas1SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                          xgbMeas2SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                           xgbMeas3SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                           xgbMeas4SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                           xgbMeas5SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                           xgbMeas6SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                           xgbMeas7SmotedSelectedCv$evaluation_log$test_auc_mean[3]),
                          "Diff. Between Dates Selected AUC" = c(NA,
                                                                   xgbDiff1SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                                   xgbDiff2SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                                   xgbDiff3SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                                   xgbDiff4SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                                   xgbDiff5SmotedSelectedCv$evaluation_log$test_auc_mean[3],
                                                                   xgbDiff6SmotedSelectedCv$evaluation_log$test_auc_mean[3]))
opts <- options(knitr.kable.NA = "-")
kable(xgb.metrics, align = "c", digits = 2, caption = "XGBoost Model Metrics", col.names = c("Days after Thinner",
                                                                                             "Single Date Error",
                                                                                             "Single Date SMOTE Error", 
                                                                                             "Diff. Between Dates Error",
                                                                                             "Diff. Between Dates SMOTE Error",
                                                                                             "Single Date Selected Error",
                                                                                             "Diff. Between Dates Selected Error",
                                                                                             "Single Date AUC",
                                                                                             "Single Date SMOTE AUC", 
                                                                                             "Diff. Between Dates AUC",
                                                                                             "Diff. Between Dates SMOTE AUC",
                                                                                             "Single Date Selected AUC",
                                                                                             "Diff. Between Dates Selected AUC"))
```